---
title: "Data Check"
author: "Arnob Alam"
date: "January 11, 2017"
output: html_document
vignette: >
  %\VignetteIndexEntry{Data Check}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose
The purpose of this vignette is to check the Nyakatoke village data provided
in (source) and compare descriptive statistics with what is stated in published
works.

## Data loading/saving

This part of the code is simply loads the raw data in the extdata folder and
saves it as an R data set

```{r datamunging}
baseLoc <- system.file(package="riskSharing") 
extPath <- file.path(baseLoc, "extdata") 
```

```{r nyakatoke_data, eval=FALSE}
nyakatoke <- read.csv(file.path(extPath, file.path("tanzania_data.csv")))
save(nyakatoke, file = "../data/nyakatoke.RData", compress = "xz")
```

# Ananlysis

We load the igraph package and reload the data

```{r loadData}
library(riskSharing)
data("nyakatoke")
```

## Recreate DeWeerdt (2006)

Let's create an undirected graph from the data.  In this case, we say two 
households share a link if either household reported the other.

```{r create_graph}
library(igraph)
g <- graph_from_data_frame(nyakatoke[nyakatoke$willingness_link1 == 1 |
                                nyakatoke$willingness_link2,], directed = FALSE)
g <- simplify(g)
```

```{r base_stats}
library(xtable)
g.order <- length(igraph::V(g))
g.size <- length(igraph::E(g))
g.mean.degree <- mean(degree(g))
g.min.degree <- min(degree(g))
g.max.degree <- max(degree(g))
g.distances <- distance_table(g)$res
names(g.distances) <- 1:length(g.distances)
summary.stats <- data.frame("graph order" = g.order,
                            "graph size" = g.size)
print(xtable(summary.stats), type="html")
```
